Report

### 2021-03-08 Rmd/report.Rmd
Add report

---
title: "Report"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "100%",
	results = "asis"
)
options(knitr.kable.NA = '-')

@@

# load packages
library(papaja)
library(knitr)
library(data.table)
library(dplyr)
library(magrittr)
library(readxl)
library(tidyr)
library(tibble)
library(ggplot2)
library(lubridate)
library(patchwork)
library(here)

@@

# Procedure

# Stimuli

## Duration

## Intensity

## Pitch/F0

## Lexical frequency

# Sample

We tested `r distinct(participants, participant) %>% nrow()` participants, of which `r data.sample %>% filter(!Pilot, DateTest<now(), !Valid) %>% pull(ID) %>% length() %>% printnum(digits = 0)` were excluded. The final sample included `r data.sample %>% filter(!Pilot, DateTest<now(), Valid, LangProfile=="Monolingual") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` monolinguals (`r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Monolingual", Language=="Catalan") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Catalan monolinguals, `r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Monolingual", Language=="Spanish") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Spanish monolinguals) and `r data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Bilingual") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` bilinguals (`r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Bilingual", Language=="Catalan") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Catalan-dominant, `r  data.sample %>% filter(!Pilot, DateTest < now(), Valid, LangProfile=="Bilingual", Language=="Spanish") %>% pull(ID) %>% unique() %>% length() %>% printnum(digits = 0)` Spanish-dominant).

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

data.sample %>%
	filter(!Pilot, Valid, DateTest<now()) %>%
	select(ID, LangProfile, AgeGroup, Language, List, Sex) %>%
	group_by(LangProfile, AgeGroup, Language, List) %>%
	summarise(n = n()) %>%
	pivot_wider(id_cols = c("LangProfile", "AgeGroup", "Language"), names_from = "List", values_from = "n") %>%
	mutate(Total = sum(`1`, `2`, `3`, na.rm = TRUE)) %>%

	kable(digits = 0,
		  col.names = c("***LP***", "**Age group**", "**Language**", "**List 1**", "**List 2**", "**List 3**", "**Total**"), 
		  align = "c",
		  caption = "Sample size by age group, testing language, and list. Only participants that made it in the final sample are included.")

@@

## Trackloss

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

attrition %>%
	left_join(data.sample, by = c("ParticipantID" = "ID")) %>%
	summarise(
		TracklossForParticipant = first(TracklossForParticipant),
		TracklossForParticipantSD = sd(TracklossForTrial, na.rm = TRUE)
		) %>%
	mutate(TracklossForParticipant = paste(printnum(TracklossForParticipant), "%"),
		   TracklossForParticipantSD = printnum(TracklossForParticipantSD)) %>%
	arrange(ParticipantID) %>%
	kable(digits = 3,
		  row.names = FALSE,
		  align = "c",
		  col.names = c("**Participant ID**", "**Mean**", "***SD***"),
		  caption = "Mean proportion of samples lost by trial.")

@@

## Growth Curve Analysis

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

results %>%
	select(Term, Estimate, SEM, Chisq, Df, p, ci1, ci2) %>%
	mutate(CI = paste0("[", printnum(ci1, digits=2), ",", printnum(ci2, digits=2), "]"),
		   p = printp(p)) %>%
	select(-c(ci1, ci2)) %>%
	kable(
		digits = 2,
		row.names = FALSE,
		col.names = c("**Term**", "**$\\beta$**", "***SEM***", "**$\\chi^2$**", "***Df***", "***p***", "**95\\%*CI***"),
		align = "c",
		caption = "Results of the Growth Curve Analysis, reporting the estimated coefficients of the fixed effects included in the model. *p*-values were extracted using Wald's $\\chi^2$ approximation."
	)

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Coefficients of the fixed effects included in the Growth Curve Analysis. Black dots and whiskers represent the estimated coefficient and standard error of the mean, respectively. Grey boxes represent two-sided 95\\% confidence intervals, calculated using the Wald $\\chi^2$ approximation to degrees of freedom."}

include_graphics(here("Figures", "05_gca-coefficients.png"))

@@

## Predictions

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Predicted unfolding of target fixations across the time course of the trial for each participant, split by trial type, language profile, and testing language."}

include_graphics(here("Figures", "05_gca-predictions-participant.png"))

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Predicted unfolding of target fixations across the time course of the trial for each trial, split by trial type, language profile, and testing language."}

include_graphics(here("Figures", "05_gca-predictions-trial.png"))

## Variance-covariance parameters

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Variance-covariance matrix."}

include_graphics(here("Figures", "05_gca-vcov.png"))

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Correlations between random effects split by fixed effect."}

include_graphics(here("Figures", "05_gca-correlation.png"))

## Checking assumptions

### Normality

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Distribution of the observed studentised residuals, compared with the theoretical normal distribution."}

include_graphics(here("Figures", "05_gca-residuals.png"))

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.cap="Distribution of the observed studentised residuals, compared with the theoretical normal distribution."}

results %>%
	select(Term, VIF) %>%
	kable(digits = 2,
		  row.names = FALSE,
		  col.names = c("***Term***", "***VIF***"),
		  align = "c",
		  caption = "Multicollinearity" 
		  )
```

@@

## Participants

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

data.sample %>%
	filter(!Pilot, DateTest<now()) %>%
	select(ID, LangProfile, AgeGroup, Language, List, DateTest, Age, Sex, Valid) %>%
	arrange(desc(Valid), LangProfile, AgeGroup, Language, List, ID) %>%
	kable(digits = 2,
		  row.names = FALSE,
		  align = "c",
		  col.names = c("**Participant ID**", "***LP***", "**Age group**", "**Lang.**", "**List**", "**Date**", "**Age**", "**Sex**", "**Valid?**"),
		  caption = "Complete list of participants. *LP* = Language profile.")

>>>>

---
title: "Report"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	message = TRUE,
	warning = TRUE, 
	cache.extra = knitr::rand_seed,
	out.width = "100%",
	results = "asis",
	dev.args = list(png = list(type = "cairo"))
)
options(knitr.kable.NA = '-')

@@

# load packages
library(papaja)
library(knitr)
library(tidyverse)
library(readxl)
library(lubridate)
library(scales)
library(patchwork)
library(here)

# load functions
source(here("R", "utils.R"))

@@

# Participants

```{r participants, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
# plot participants
participants %>% 
	drop_na() %>% 
	ggplot(aes(lp, fill = valid_participant)) +
	facet_grid(~age_group) +
	geom_bar() +
	geom_hline(yintercept = 24, linetype = "dashed") +
	labs(x = "Group", y = "N", fill = "Valid?") +
	scale_fill_brewer(palette = "Set1") +
	theme_custom() +
	theme(axis.title.x = element_blank()) +
	ggsave(here("Figures", "sample.png"))
```

## Attrition rate

```{r attrition, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=12}

col <- ifelse(distinct(attrition, participant, valid_participant)$valid_participant, "#377EB8", "#E41A1C")

attrition %>% 
	mutate(valid_trial = ifelse(valid_trial, "Valid", "Invalid"),
		   participant = paste0(participant, " (", missing_n, ", ", percent(missing_prop), ")")) %>% 
	ggplot(aes(missing, participant, colour = valid_trial)) +
	geom_point(alpha = 0.5) +
	geom_vline(xintercept = 0.25, linetype = "dashed") +
	labs(x = "Proportion of missing trials (out of 32)", y = "Participant") +
	scale_color_brewer(palette = "Set1") +
	theme_custom() +
	theme(axis.text.y = element_text(colour = col, size = 8),
		  axis.title.y = element_blank(),
		  axis.text.x = element_text(colour = "black"),
		  legend.title = element_blank(),
		  legend.position = "top",
		  text = element_text(size = 15)) +
	ggsave(here("Figures", "missing.png"), height = 9)

@@

## Vocabulary

```{r vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=4}
# vocabulary
participants %>% 
	mutate(age_group = as.factor(age_group)) %>% 
	drop_na(lp) %>% 
	ggplot(aes(as.factor(age_group), vocab_size, colour = lp, fill = lp)) +
	geom_point(shape = 1, size = 3, stroke = 1, position = position_jitter(width = 0.1, seed = 888)) +
	geom_boxplot(width = 0.1, colour = "black", outlier.colour = NA, position = position_dodge(width = 0.75)) +
	labs(x = "Age group (months)", y = "Receptive vocabulary size (L1)", colour = "Group", fill = "Group") +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_custom() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "vocabulary.png"))

@@

## Target fixations

### Aggregated by trial

```{r gaze_trial, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group) %>% 
	summarise(prop = mean(prop), .groups = "drop") %>% 
	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_boxplot(width = 0.1, colour = "black", fill = "white", position = position_nudge(x = 0.2), outlier.colour = NA) +
	geom_point(size = 2, shape = 1, stroke = 1) +
	labs(x = "Condition", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_colour_brewer(palette = "Set1") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_custom() +
	theme(legend.position = "none",
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_trial.png"))

@@

```{r gaze_trial_vocabulary, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_trial %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, lp, trial_type, age_group, vocab_size) %>% 
	summarise(prop = mean(prop), .groups = "drop") %>% 
	ggplot(aes(vocab_size, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_line(aes(group = participant), colour = "grey", alpha = 0.5) +
	#stat_slab(position = position_nudge(x = 0.25)) +
	geom_point(size = 2, shape = 1, stroke = 1) +
	geom_smooth(se = FALSE, method = "lm") +
	labs(x = "L1 vocabulary size", y = "Target looking / Total looking", colour = "Condition", fill = "Condition") + 
	scale_colour_brewer(palette = "Set1") +
	scale_x_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	theme_custom() +
	theme(legend.position = "none",
		  panel.grid.major.y = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_trial_vocabulary.png"))
```

### Aggregated by time bin

```{r gaze_time, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
gaze_time %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(time_bin, trial_type, lp, age_group) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se
	) %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	geom_point(shape = 1, stroke = 1, size = 1) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_custom() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted")) +
	ggsave(here("Figures", "gaze_time.png"))

@@

```{r gaze_time_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8}
gaze_time %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, time_bin, trial_type, lp, age_group) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se
	) %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_wrap(age_group~participant~lp) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	geom_point(shape = 1, stroke = 1, size = 0.5) +
	geom_text(aes(x = 0, y = 1, label =
				  	paste0(str_remove_all(participant, pattern = "[a-zA-Z]"),
				  		   "/", age_group, "mo/", lp)),
			  size = 2, colour = "black", hjust = 0) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_custom() +
	theme(
		axis.text = element_text(size = 7),
		legend.title = element_blank(),
		legend.position = "top",
		strip.background = element_blank(),
		strip.text.x = element_blank()
	) +
	ggsave(here("Figures", "gaze_time_participant.png"), height = 12, width = 12)
```

@@
